\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
% \usepackage{charter}
\usepackage{mathpazo}
\usepackage{ragged2e}
\input{glyphtounicode}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% % Margins
\usepackage[margin=0.4in]{geometry}


% Basic settings
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.08003pt}
\setlength{\footskip}{4.08003pt}

% Section formatting
\titleformat{\section}{
  \vspace{3pt}
  \scshape\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% PDF settings
\pdfgentounicode=1

% Custom commands


\newcommand{\resumeItem}[1]{
\justifying
  \item{\small{#1}}
  \vspace{-2px}
}

% % \textbf{-}
% \newcommand{\resumeProject}[2]{
% \justifying
%   \item{\small{\textbf{\small{#1}}}: {#2}}
% }

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\large{#1}} & {\small{#2}} \\
      {\textsl{{#3}}} & {\textsl{\small{#4}}}
    \end{tabular*}
  \vspace{-0.5cm}
}

% List environment commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\renewcommand\labelitemii{$\vcenter{\hbox{$\bullet$}}$}
\newcommand{\resumeItemListStart}{
  \vspace{-5pt}
  \begin{itemize}[leftmargin=0.21in, label=\textbullet]
}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% Header/Contact Information
\def\name{Vishwanath (Vish) Guruvayur}
\def\phone{+1 (571) 602-2034}
\def\city{Gainesville, VA}
\def\email{vishguru2704@gmail.com}
\def\LinkedIn{vishgp}
\def\github{vishugp}
\def\role{Data Scientist II}


\begin{center}
    % \href{https://vishugp.github.io/Resume}
    {\huge \textbf{\fontsize{24pt}{13pt}\selectfont{\name}}}\\
    \vspace{0.05cm}
    {\huge{\role}}
\end{center}

\vspace{-52pt}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \footnotesize
    \begin{minipage}[t]{0.4\textwidth}
        \city\\
        \href{tel:\phone}{+1 (571) 602-2034}\\
        \href{mailto:\email}{\email}
    \end{minipage} 
    &
    \begin{minipage}[t]{0.4\textwidth}\raggedleft
    \footnotesize
    
        \href{https://vishguru.com}{{vishguru.com}}\\
        \href{https://github.com/\github}{{github.com/\github}}\\
        \href{https://www.linkedin.com/in/\LinkedIn}{{linkedin.com/in/\LinkedIn}}\\
        
    \end{minipage}
\end{tabular*}


%----------- PROFESSIONAL EXPERIENCE -----------
\vspace{-9pt}
\section{\Large{Experience}}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
    {Machine Learning Researcher}
    {Tysons, VA (Remote)}
    {LMI Inc. and UVA School of Data Science}
    {Nov 2024 -- Apr 2025}
\vspace{1pt}
\resumeItem{Led end-to-end development of a multimodal RAG-based LLM product for educational content retrieval, from conceptualization to deployment, achieving high adoption in academic settings.}
\resumeItemListStart
\resumeItem{Developed an \textbf{end-to-end multimodal RAG pipeline} using Python, SQL, Sentence Transformers, and CLIP embeddings, indexing over \textbf{6,000 vectors} from educational text, images, and audio for semantic retrieval via Pinecone DB.}
\resumeItem{Evaluated three RAG frameworks (Zero-Shot, Text-only, Image-augmented) to enhance retrieval accuracy and summarization quality, presenting results to academic and technical stakeholders for strategic adoption.}
\resumeItem{\textbf{Awarded “Most Compelling Data Visualizations”} at the Capstone Showcase for designing intuitive Plotly Graphs with semantic clustering, improving  understanding of LLM RAG System.}
\resumeItemListEnd

\vspace{-3pt}
\resumeSubheading
    {Lead Data Scientist}
    {Bethlehem, PA (Remote, Mumbai Office)}
    {Piramal Pharma Ltd.}
    {Jan 2022 -- Jun 2024}
\vspace{1pt}
\resumeItem{\textbf{Led a high-performing Data Science and Analytics Team}, driving data-driven product development and strategic analytics for financial planning and market expansion, influencing C-suite decisions.}
\resumeItemListStart
\resumeItem{\textbf{Saved \$1.2M quarterly} by developing a time-series forecasting product using S-ARIMA and Monte Carlo simulations in Python and SQL, optimizing inventory replenishment cycles and enhancing financial visibility.}
\resumeItem{\textbf{Collaborated with CFO to launch market expansion initiatives} by designing Power BI and Plotly Dash analytics dashboards, integrating market data, segmentation, and competitive intelligence for strategic financial planning.}
\resumeItem{\textbf{Received “Piramal Excellence Award”} for building over \textbf{30 SQL-driven analytics pipelines} using Python and Azure Databricks, reducing reporting turnaround from monthly to daily and boosting efficiency by 85\%.}
\resumeItem{\textbf{Drove talent development strategies} by developing an NLP-based product using VADER sentiment analysis and topic modeling, enabling CHRO to personalize growth plans and improve retention.}
\resumeItemListEnd

\vspace{-1pt}
\resumeSubheading
    {Data Science Intern}
    {Mumbai, India}
    {Piramal Pharma Ltd.}
    {Jul 2021 -- Dec 2021}
\vspace{1pt}
\resumeItem{Developed and launched data-driven products to enhance market penetration and employee retention, collaborating with business and technical teams.}
\resumeItemListStart
\resumeItem{Built the company’s first \textbf{product recommendation engine} using the FP-Growth algorithm in Python and SQL, driving a \textbf{15\% quarterly increase in market penetration} across 400,000 retailers.}
\resumeItem{Developed an \textbf{attrition prediction product} using XGBoost and Logistic Regression, achieving \textbf{93\% retention of high-performing sales reps} and informing HR strategies.}
\resumeItem{Recognized by the CEO for impactful product development, leading to an offer to head a \textbf{new analytics team.}}
\resumeItemListEnd
\resumeSubHeadingListEnd









%----------- SKILLS -----------
\vspace{-15pt}
\section{\Large{Skills}}
\vspace{3pt}
\begin{itemize}[leftmargin=0.00in, label={}, itemsep=0pt, parsep=0pt]
    \item{
        \small{\textbf{Languages:}}
        \small{Python, R, SQL, JavaScript} 
        % \hfill
        \hspace{0.7cm}
        {\fontseries{b}\fontsize{10.2pt}{13pt}\selectfont{Tools:}}
        \small{Bash, Docker, Git, Conda, Jupyter, MLflow, Kubeflow}
        }

        % /, JavaScript, C++, MATLAB, Scala, Julia

    % \item{
    %     {\fontseries{b}\fontsize{10.2pt}{13pt}\selectfont{Machine Learning:}}
    %     \small{Supervised (Regression, Classification), Unsupervised (Clustering, Association Rules Mining)}
    %     }

    %     \item{
    %     {\fontseries{b}\fontsize{10.2pt}{13pt}\selectfont{Artificial Intelligence:}}
    %     \small{Deep Learning (PyTorch, TensorFlow), NLP and LLMs (LangChain, HuggingFace)}
    %     }

    \item{
        \small{\textbf{AI and ML:}}
        \small{Machine Learning (Scikit-Learn), Deep Learning (PyTorch, TensorFlow), LLMs (LangChain), NLP (NLTK, SpaCy)}
        }

    \item{
        \small{\textbf{Visualization:}}
        \small{Power BI, Plotly Dash, Matplotlib, GGPlot, d3.js, QlikSense}
        }
        
    \item{
        \small{\textbf{Big Data and Cloud:}}
        \small{Spark, AWS (SageMaker, EC2, S3), Azure (DataBricks, Data Factory), Snowflake}
        }

    
    % \item{
    % \small{\textbf{Interests and Hobbies:}}
    % \small{Singing and enjoying music - \href{https://vishuragams.pages.dev}{\underline{Carnatic Ragas}}, playing \href{https://vishugp.github.io/Thuruppu/}{\underline{card games}} and badminton, robotics}
    % }
\end{itemize}



%-----------EDUCATION----------
\vspace{-16pt}
\section{\Large{Education}}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
    {University of Virginia}{Charlottesville, VA}
    {Master of Science in Data Science, GPA: 4.0/4.0}{Jun 2024 -- May 2025}

\vspace{6px}
% {\fontseries{}\fontsize{10.2pt}{11pt}\selectfont{Activities:}}
\footnotesize{
Teaching Assistant - Statistical Machine Learning {\textbullet}
Data Science Ambassador {\textbullet}
Academic Village Resident (The Range)\\



% \textbf{\textsl{Coursework:}}
% Large Language Models (LLMs) {\textbullet}
% Statistical and Bayesian Machine Learning (ML) {\textbullet} 
% Big Data Systems (Cloud Architecture) {\textbullet}
% Deep Learning (DL) {\textbullet}
% Natural Language Processing (NLP) {\textbullet}
% Data Structures and Algorithms (DSA) {\textbullet}
% Data Engineering {\textbullet}
% % Bayesian Machine Learning {\textbullet}
% Data Ethics 

}



\resumeSubHeadingListEnd
\vspace{-8pt}
\resumeSubHeadingListStart
\resumeSubheading
    {Birla Institute of Technology and Science \normalsize{(BITS Pilani)}}{Hyderabad, India}
    {Bachelor of Engineering in Mechanical Engineering, Minor in Data Science, GPA: 3.8/4.0}{Aug 2018 -- Dec 2021}

\resumeSubHeadingListEnd

\setlist[itemize]{leftmargin=0.38cm}



%-----------CERTIFICATIONS-----------
\vspace{-9pt}
\section{\Large{Certifications}}
\vspace{9pt}
\resumeItemListStart

\resumeItem{AWS Certified Solutions Architect – Associate, \textsl{Amazon Web Services}\hfill\sl{May 2025 - May 2028}}

\resumeItem{\vspace{-8pt}AWS Certified Machine Learning – Specialty, \textsl{Amazon Web Services} \hfill\sl{In Progress, Scheduled Jun 2025}}

\resumeItemListEnd

\end{document}