%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letter paper,11pt]{article}

\usepackage{latexsym}

\usepackage[empty]{fullpage}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% \setlist[itemize]{noitemsep}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.08003pt}
\setlength{\footskip}{4.08003pt}
% \newlist{myEnumerate}{itemize}{6}
% \setlist[myEnumerate]{nosep,label=\protect\mpbullet}
% \setlistdepth{6}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\justifying
\vspace{-2.89pt}
  \item\small{
    {#1}
  }
}

% \newcommand{\resumeSubheading}[4]{
%   \vspace{-2pt}\item
%     \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{\small#3} & \textit{\small #4} \\
%     \end{tabular*}\vspace{-7pt}
% }

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubheading}[5]{%
% \vspace{0.1cm}%
  \item
    \begin{tabular*}
    {1\textwidth}
    {l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small#2 \\
      {\small#3} & {\small #4} \\
      {\small#5}
    \end{tabular*}%
  \vspace{-0.8cm}
}


\newcommand{\resumeProjectHeading}[4]{
% \vspace{-12pt}
    \vspace{-0.2cm}
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small#2} \\
      {\small#3} & {\small#4}
    \end{tabular*}\vspace{-13pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING-----------------


\begin{center}
    \textbf{\Huge \scshape Vishwanath Guruvayur} \\ 
    \vspace{7pt}
    \small 
    \href{tel:+1 (571) 602-2034}{\underline{+1 (571) 602-2034}} $|$ \href{mailto:vishvesh2704@gmail.com}{\underline{vishguru2704@gmail.com}} $|$ 
    \href{https://linkedin.com/in/vishgp}{\underline{linkedin.com/in/vishgp}} $|$
    \href{https://github.com/vishugp}{\underline{github.com/vishugp}} $|$
    \href{https://vishugp.github.io}{\underline{vishugp.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
         {\textbf{University of Virginia}}{Charlottesville, VA}
        {Master of Science in Data Science}{Jun. 2024 -- May. 2025}{}

        \item\small{{\textit{\textbf{{Relevant Coursework}}}}}
        \vspace{-0.25cm}
    \justifying
    \begin{itemize}[leftmargin=0.00in, label={}]
    \small{\item{ 
    Bayesian Machine Learning
    \textbullet{} Statistical Learning
    \textbullet{} Linear Models for Data Science
    \textbullet{} Ethics in Big Data
    \textbullet{} Foundations of Computer Science
    \textbullet{} Practical Applications of Data Science
    
    % \textbullet{} Linear Algebra
    % \textbullet{} Calculus
    % \textbullet{} Control Systems
    }}
 \end{itemize}

 \vspace{0.05cm}
        
    \resumeSubheading
        {\textbf{Birla Institute of Technology \& Science, Pilani (BITS Pilani)}}{Hyderabad, India}
        {Bachelor of Engineering in Mechanical Engineering, Minor in Data Science}{Aug. 2018 -- Dec. 2022}{}


 \resumeSubHeadingListEnd 
%
%----------- SKILLS-----------
\section{Skills}
% \vspace{3pt}
 \begin{itemize}[leftmargin=0.00in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, R, SQL, C/C++, MATLAB, Julia} \\
     % \vspace{1pt}
     \textbf{Machine Learning \& AI}{: PyTorch, Keras, TensorFlow, Random Forests, FP-Growth, OpenCV} \\
     % \vspace{1pt}
     \textbf{Data \& BI Tools}{: Python (Pandas, NumPy), Azure DataBricks, MS Excel, PowerBI, Docker, SPSS}
    }}
 \end{itemize}
 
\setlist[itemize]{leftmargin=0.38cm}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Piramal Critical Care (PCC)}
    {Bethlehem, PA (Remote, India)}
    {Data Science Lead}
    {Jan. 2022 -- Jun. 2024}{}
    % \vspace{1pt}

    \resumeItemListStart
    
    \resumeItem {\textbf{Led the Data Science \& Analytics Team} to drive business growth by integrating data-driven strategies across Supply Chain, Demand Planning, Finance, and Sales Operations.}

    \resumeItem{Implemented multiple \textbf{Smart Automation Frameworks}, increasing data accuracy and reducing manual reporting work by \textbf{60\%} through end-to-end automation and advanced visualizations.}
    
    \resumeItem{Delivered \textbf{Descriptive \& Predictive Analytics} in various projects leveraging ML techniques to uncover sales and supply chain patterns to forecast Market Share trends and prevent potential Material Stock-outs.}
    \resumeItemListEnd


    \resumeSubheading
    {\textbf{Piramal - Consumer Product Division (CPD)}}{Mumbai, India}
      {Data Science Intern}{Jul. 2021 -- Dec. 2021}
      {}\vspace{1pt}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Sales Recommendation Engine} using the FP-Growth Algorithm, optimizing product reach for over 300,000 retailers across India. Implemented a tracking system to refine the recommendations resulting in \textbf{15\% Market Growth}.}
        
        \resumeItem{Created an Ensemble Predictive Model of Random Forest and Logistic Regression to predict Sales Officer's Attrition. Worked with the HR Team to create a feedback mechanism, which improved prediction accuracy and employee retention rates by \textbf{20\%}.}
        
    \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
\vspace{0.2cm}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Inventory Management Analytics \& Forecasting}}
          {Piramal Critical Care}
          {Machine Learning, Analytics $|$ Supply Chain \& Finance }
          {Jun. 2023 - Jun. 2024}
          
          \resumeItemListStart
            \resumeItem{Created an inventory consumption forecasting model incorporating scenario planning and demand forecasting aimed at reducing monthly provisional write-offs worth around \$70k by optimizing inventory management for aging and expiring stock categories}
          \resumeItemListEnd
          
     \resumeProjectHeading
          {\textbf{Piramal Sales Market Share \& Growth Analytics}}
          {Piramal Critical Care}
          {Machine Learning, Analytics $|$ Finance \& Sales}
          {May. 2023 - Dec. 2023}
          
          \resumeItemListStart
            \resumeItem{Developed market share and growth analytics for the injectable pain market, utilizing advanced statistical metrics to classify markets by competitiveness, growth, and portfolio diversity, driving key long-term business decisions.}
          \resumeItemListEnd

      
           \resumeProjectHeading
          {\textbf{Sentiment Analysis Modelling of Employee's Feedback Texts}}
          {Piramal CPD}
          {Natural Language Processing $|$ Human Resources}
          {Oct. 2021 - Dec. 2022}
          
          \resumeItemListStart
            \resumeItem{Built an ensemble NLP model leveraging VADER Sentiment and TextBlob to analyze employee feedback, identify key development areas, and assign personalized development plans based on sentiment analysis.}
          \resumeItemListEnd
          
    
          
      


    \resumeProjectHeading
          {\textbf{Emotion Recognition using Genetic Algorithm} } {BITS Pilani}
          {Artificial Intelligence, Computer Vision $|$ Artificial Intelligence Course}
          {Jan 2021 - Jun 2021}
          
          \resumeItemListStart
            \resumeItem{Worked on implementing the Genetic Algorithm to identify the emotion of a masked face from a set of emotions using the OpenFace Toolkit for facial landmark detection.}
          \resumeItemListEnd


    
    % \resumeProjectHeading
    %       {\textbf{Live Obstacle Tracking for Robotic Reinforcement Learning Systems}}{BITS Pilani}
    %       {Artificial Intelligence $|$ Applied AI in Robotics Project}{Aug 2020 - Dec 2020}
          
    %       \resumeItemListStart
    %         \resumeItem{Developed a live interpretation of the robotics visual perception with optimal detection of obstacles with the knowledge of the obstacle velocity and acceleration using OpenCV and Gazebo Simulator.}
    %       \resumeItemListEnd


          
    \resumeSubHeadingListEnd
    

%-------------------------------------------
\end{document}