\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}



% \usepackage{mathpazo}
% \usepackage{libertine}
% \usepackage{charter}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{sourcesanspro}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{ragged2e}
\input{glyphtounicode}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% % Margins
\usepackage[margin=0.45in]{geometry}


% Basic settings
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.08003pt}
\setlength{\footskip}{4.08003pt}

% Section formatting
\titleformat{\section}{\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule]

% PDF settings
\pdfgentounicode=1

% Custom commands


\newcommand{\resumeItem}[1]{
% \justifying
  \item{\small{#1}}
  \vspace{-1.5px}
}

% % \textbf{-}
% \newcommand{\resumeProject}[2]{
% \justifying
%   \item{\small{\textbf{\small{#1}}}: {#2}}
% }

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\large{#1}} & {\small{#2}} \\
      {{{#3}}} & {{\small{#4}}}
    \end{tabular*}
  \vspace{-0.4cm}
}

% List environment commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\renewcommand\labelitemii{$\vcenter{\hbox{$\bullet$}}$}
\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=0.18in, label=\textbullet]
}
\newcommand{\resumeItemListEnd}{\end{itemize}}


%------------------------------------------------------------


\def\Summary{\small{
Data Scientist with \textbf{3+ years of experience} building ML systems and data products across healthcare, operations, and e-commerce. Expertise in \textbf{Python, SQL, and AWS}, delivering production-grade, interpretable data products with model monitoring expertise. Strong focus on scalable deployment, experimentation, and \textbf{LLM-based retrieval}, with peer-reviewed research in multimodal RAG. Passionate about \textbf{bridging research and real-world impact} through responsible, scalable data science products.
}}


%------------------------------------------------------------

\begin{document}


% Header/Contact Information
\def\name{Vishwanath (Vish) Guruvayur}
\def\phone{+1 (571) 602-2034}
\def\city{Gainesville, VA}
\def\email{vishguru2704@gmail.com}
\def\LinkedIn{linkedin.com/in/vishgp}
\def\github{vishugp}
\def\role{Data Scientist}
\def\paperlink{https://intextbooks.science.uu.nl/workshop2025/files/iTextbooks2025_paper_3.pdf}
\def\salink{https://www.credly.com/badges/12da6e0d-aa6a-4a6e-a598-93941c4a35c6}
\def\mllink{https://www.credly.com/badges/c8b32ca5-03da-4578-a92f-9e11d0011ee8}

\vspace*{-30pt}
\begin{center}
    {\Huge{\name}}
    \vspace{3pt}

    
    \small 
    \href{https://vishguru.com}{{vishguru.com}} $|$
    \href{tel:+1 (571) 602-2034}{\phone} $|$ 
    \href{mailto:vishvesh2704@gmail.com}{{\email}} $|$ 
    \href{https://linkedin.com/in/vishgp}{\LinkedIn}
    
\end{center}


\vspace{-27pt}
% \justifying
\section{Summary}
\vspace{-5pt}
\Summary
\vspace{-12pt}

%-------------------EXPERIENCE---------------------------
\section{Experience}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeSubheading
    {AI Researcher}
    {Charlottesville, VA (Remote)}
    {University of Virginia}
    {Nov 2024 - Present}
    
    \resumeItemListStart
    \resumeItem{Leading \textbf{applied research on multimodal and hybrid RAG} (Retrieval-Augmented Generation) to enhance content retrieval, comprehension and semantic search across educational media in the form of text, image, and audio.}

    \resumeItem{Built and evaluated a scalable RAG \textbf{pipeline with 10,000+ multimodal vectors} using SentenceTransformers, CLIP, and Pinecone, and evaluation using RAGAS and adversarial prompts to improve retrieval accuracy and reduce hallucination.}

    \resumeItem{Co-authored  \href{\paperlink}{\textbf{peer-reviewed paper} {\underline{link}}} at AIED 2025 conference, introducing innovative techniques for multimodal retrieval and evaluation; awarded “Most Compelling Data Visualizations” at UVA's Annual Capstone Showcase.}


    \resumeItem{Currently leading R\&D of an \textbf{Agentic AI-based LLM assistant} that leverages structured retrieval over temporally-linked academic content to explore new methods of enhancing student support and informing instructional strategy.}

    
    \resumeItemListEnd


\resumeSubheading
    {Senior Data Scientist}
    {Bethlehem, PA (Remote)}
    {Piramal Pharma Ltd.}
    {Jan 2022 - Jun 2024}

    \resumeItemListStart
    \resumeItem{\textbf{Established and led the Data Science team} for the Critical Care division, driving analytics integration into key business functions and mentoring junior data scientists across multiple high-impact projects.}

    \resumeItem{\textbf{Prevented \$1.2M in quarterly inventory losses} by implementing counterfactual analysis of consumed inventory, write-offs and forecasted sales forecasting using Monte Carlo simulations and S-ARIMA modeling.}

    \resumeItem{Worked closely with the CFO to develop market segmentation models and competitive intelligence dashboards using AWS and PowerBI, guiding global pricing, product launch, and acquisition strategies across 5 business regions.}

    \resumeItem{Reduced ACoS \textbf{from 45\% to 8\% within 6 months} for high-priority e-commerce products by leveraging alternative data with NLP (VADER, SpaCy), market segmentation, and A/B testing to boost ad campaign optimizations.}

    \resumeItem{\textbf{Enabled CHRO led initiatives} to assign targeted development plans and improve employee retention by building an NLP-based sentiment analytics pipeline with VADER and TextBlob to analyze employee performance reviews.}

    \resumeItem{Received the “Piramal Excellence Award” for building \textbf{30+ ML and analytics pipelines} with workflows for monitoring for model health for retraining triggers and business KPIs for performance reporting, improving operational efficiency by 85\%.}
    
    \resumeItemListEnd

\resumeSubheading
    {Data Scientist}
    {Mumbai, India}
    {Piramal Pharma Ltd.}
    {Jul 2021 - Dec 2021}

    \resumeItemListStart
    \resumeItem{Intern in the Consumer Products division, delivering data science projects with high-impact in business-facing initiatives.}

    \resumeItem{Built the company's first product recommendation engine and coded the Tree-based FP-Growth algorithm from scratch, achieving a \textbf{15\% quarterly increase} in market penetration across \textbf{400,000 retailers}.}

    \resumeItem{Boosted high-performing sales reps \textbf{retention rates to 93\%} by developing an attrition prediction model using XGBoost and Logistic Regression on historic sales performance and past employee data.}

    % \resumeItem{Recognized for impact by the CEO and offered a leadership role to build and head a new data science team.}
    \resumeItemListEnd
    

\resumeSubHeadingListEnd

%----------------- CERTIFICATIONS -----------------
\vspace{-18pt}
\section{\normalsize{C}\small{ERTIFICATIONS}}
\vspace{-7pt}
\resumeItemListStart
\resumeItem{
\href{\salink}
{\textsl{AWS Certified Solutions Architect – Associate, Amazon Web Services}}\hfill\sl{May 2025 - May 2028}}
\vspace{-5pt}
\resumeItem{
\href{\mllink}{\textsl{AWS Certified Machine Learning – Specialty, Amazon Web Services}} \hfill\sl{Jun 2025 - Jun 2028}}
\resumeItemListEnd


%-------------------EDUCATION---------------------
\vspace{-18pt}
\section{Education}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeSubheading
    {University of Virginia {(UVA)}}
    {Charlottesville, VA}
    {Master of Science in Data Science, GPA: 4.0/4.0}
    {Jun 2024 - May 2025}

    % \vspace{5pt}
    % \footnotesize{
    % Data Science Ambassador {\textbullet}
    % Teaching Assistant - Statistical Learning {\textbullet}
    % Range Resident
    % }

    \vspace{10pt}
    % \small{{Certifications:}
    % {\href{\salink}
    % {\textsl{AWS Solutions Architect - Associate}}},
    % {\href{\mllink}
    % {\textsl{AWS Machine Learning - Specialty}}}}
    


\resumeSubheading
    {Birla Institute of Technology and Science \normalsize{(BITS Pilani)}}
    {Hyderabad, India}
    {B.E. Mechanical Engineering, Minor in Data Science, GPA: 3.8/4.0}
    {Aug 2018 - Dec 2021}
\resumeSubHeadingListEnd
\vspace{-14pt}

%----------------- SKILLS ------------------------
\section{Skills}
\vspace{-7pt}
\begin{itemize}[leftmargin=0.00in, label={}, itemsep=0pt, parsep=0pt]
\item{
{\textbf{Languages:} Python, R, SQL, Scala, JavaScript, Bash}
}

\item{
{\textbf{LLMs \& GenAI:} Transformers, LangChain, HuggingFace, RAG, Prompt Engineering, PEFT (LoRA, IA3), Fine-tuning
}}

\item{
{\textbf{Machine Learning:} Sklearn, XGBoost, LightGBM, NLP (SpaCy, VADER), Statistical Modeling, A/B Testing, Recommendation Engines
}}

\item{
{\textbf{Cloud and Tools:} AWS (Certified), Azure,  Databricks, Snowflake, Git, Conda, Flask}
}

\item{
\small{\textbf{Data Engineering}: Apache Spark, Snowflake, Hadoop, MLflow, Airflow, Docker, APIs, Web Scraping}
}

\item{
\small{\textbf{Visualization:} Power BI, Plotly Dash, Seaborn, Matplotlib}
}

\end{itemize}



%-------------------EOD-----------------------------
\end{document}