\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{mathpazo}
\usepackage{ragged2e}
\input{glyphtounicode}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.4in]{geometry}

% Basic settings
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.08003pt}
\setlength{\footskip}{4.08003pt}

% Section formatting
\titleformat{\section}{
  \vspace{3pt}
  \scshape\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% PDF settings
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
\justifying
  \item{\small{#1}}
  \vspace{-2px}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\large{#1}} & {\small{#2}} \\
      {\textsl{{#3}}} & {\textsl{\small{#4}}}
    \end{tabular*}
  \vspace{-0.5cm}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\renewcommand\labelitemii{$\vcenter{\hbox{$\bullet$}}$}
\newcommand{\resumeItemListStart}{
  \vspace{-5pt}
  \begin{itemize}[leftmargin=0.21in, label=\textbullet]
}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% Header/Contact Information
\def\name{Vishwanath (Vish) Guruvayur}
\def\phone{+1 (571) 602-2034}
\def\city{Charlottesville, VA}
\def\email{vishguru2704@gmail.com}
\def\LinkedIn{vishgp}
\def\github{vishugp}
\def\role{Data Scientist}

\begin{center}
    {\huge \textbf{\fontsize{24pt}{13pt}\selectfont{\name}}}\\
    \vspace{0.05cm}
    {\huge{\role}}
\end{center}

\vspace{-47pt}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \footnotesize
    \begin{minipage}[t]{0.4\textwidth}
        \city\\
        \href{tel:\phone}{\phone}\\
        \href{mailto:\email}{\email}
    \end{minipage} 
    &
    \begin{minipage}[t]{0.4\textwidth}\raggedleft
    \footnotesize
        \href{https://github.com/\github}{{github.com/\github}}\\
        \href{https://www.linkedin.com/in/\LinkedIn}{{linkedin.com/in/\LinkedIn}}\\
        \href{https://vishugp.github.io}{{Website: vishugp.github.io}}
    \end{minipage}
\end{tabular*}

%-----------EDUCATION----------
\vspace{-12pt}
\section{\Large{Education}}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubheading
    {University of Virginia}{Charlottesville, VA}
    {Master of Science in Data Science, GPA: 4.0/4.0}{Jun 2024 -- May 2025}

\vspace{6px}
\footnotesize{
Teaching Assistant - Statistical Machine Learning {\textbullet}
Data Science Ambassador {\textbullet}
Academic Village Resident (The Range)
}
\resumeSubHeadingListEnd

\vspace{-9pt}
\resumeSubHeadingListStart
\resumeSubheading
    {Birla Institute of Technology and Science (BITS Pilani)}{Hyderabad, India}
    {Bachelor of Engineering in Mechanical Engineering, Minor in Data Science, GPA: 3.8/4.0}{Aug 2018 -- Dec 2021}
\resumeSubHeadingListEnd

\setlist[itemize]{leftmargin=0.38cm}

%----------- EXPERIENCE ----------
\vspace{-9pt}
\section{\Large{Experience}}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
    {Machine Learning Researcher}
    {Tysons, VA (Remote)}
    {LMI Inc. and UVA School of Data Science}
    {Nov 2024 -- Apr 2025}
\vspace{1pt}
\resumeItem{Capstone Research on multimodal capabilities of RAG in LLMs to improve educational content retrieval and summarization.}
\resumeItemListStart
\resumeItem{Built an \textbf{end-to-end multimodal RAG pipeline} with Sentence Transformers and CLIP embeddings, indexing \textbf{over 6,000 data vectors} from diverse educational media (text, images and audio) for efficient semantic search via Pinecone DB.}
\resumeItem{Evaluated \textbf{three RAG frameworks} (Zero-Shot, Text-only, Image-augmented) on educational content, improving retrieval accuracy and summarization quality across LLaMA and GPT-4 in diverse contexts.}
\resumeItem{\textbf{Won the “Most Compelling Data Visualizations” Award} at the Capstone Showcase for clarity and impact of semantic clustering based explainability in RAG powered LLMs.}
\resumeItemListEnd

\vspace{-3pt}
\resumeSubheading
    {Lead Data Scientist}
    {Bethlehem, PA (Remote, Mumbai Office)}
    {Piramal Pharma Ltd.}
    {Jan 2022 -- Jun 2024}
\vspace{1pt}
\resumeItem{\textbf{Established and led the Data Science and Analytics Team} for the Critical Care Division, mentoring a high-performing team of 3 data scientists and integrating advanced analytics into core business functions.}
\resumeItemListStart
\resumeItem{\textbf{Prevented \$1.2M in quarterly inventory losses} by designing a time-series based supply chain forecasting system leveraging S-ARIMA and Monte Carlo simulations.}
\resumeItem{\textbf{Empowered the CFO to drive targeted market expansion strategies} through analytics dashboards combining sales data with competitive intelligence.}
\resumeItem{Received the \textbf{“Piramal Excellence Award”} for developing \textbf{30+ analytics pipelines} using Python and SQL, reducing report turnaround by 85\%.}
\resumeItem{\textbf{Enabled CHRO-led talent development initiatives} by analyzing performance reviews via VADER sentiment analysis and topic modeling.}
\resumeItemListEnd

\vspace{-1pt}
\resumeSubheading
    {Data Science Intern}
    {Mumbai, India}
    {Piramal Pharma Ltd.}
    {Jul 2021 -- Dec 2021}
\vspace{1pt}
\resumeItem{Interned in the Consumer Products Division, contributing to business-facing data science initiatives.}
\resumeItemListStart
\resumeItem{Achieved \textbf{15\% quarterly increase} in market penetration \textbf{across 400,000 retailers} by building the company’s first product recommendation engine (FP-Growth algorithm).}
\resumeItem{Boosted high-performing sales rep \textbf{retention to 93\%} via attrition prediction using XGBoost and Logistic Regression.}
\resumeItem{Recognized for impact by the CEO and \textbf{offered a leadership role to head a new analytics team}.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%----------- SKILLS -----------
\vspace{-12pt}
\section{\Large{Skills}}
\vspace{3pt}
\begin{itemize}[leftmargin=0.00in, label={}, itemsep=0pt, parsep=0pt]
    \item{
        \small{\textbf{Programming Languages:}}
        \small{Python, R, SQL, JavaScript} 
        % \hfill
        % {\fontseries{b}\fontsize{10.2pt}{13pt}\selectfont{Data Visualization:}}
        % \small{Power BI, Plotly Dash, d3.js, QlikSense}
        }
        % /, JavaScript, C++, MATLAB, Scala, Julia

    % \item{
    %     {\fontseries{b}\fontsize{10.2pt}{13pt}\selectfont{Machine Learning:}}
    %     \small{Supervised (Regression, Classification), Unsupervised (Clustering, Association Rules Mining)}
    %     }

    %     \item{
    %     {\fontseries{b}\fontsize{10.2pt}{13pt}\selectfont{Artificial Intelligence:}}
    %     \small{Deep Learning (PyTorch, TensorFlow), NLP and LLMs (LangChain, HuggingFace)}
    %     }

    \item{
        \small{\textbf{AI and ML:}}
        \small{Traditional ML (Scikit-Learn), Deep Learning (PyTorch, TensorFlow), LLMs (LangChain, HuggingFace)}
        }

    \item{
        \small{\textbf{Cloud Data Tools:}}
        \small{AWS (SageMaker, EC2, S3), Microsoft Azure (DataBricks, Data Factory, ML Studio), Git, Docker}
        }

    \item{
        \small{\textbf{Data Visualization:}}
        \small{Power BI, Plotly Dash, d3.js, QlikSense}
        }
    \item{
    \small{\textbf{Interests and Hobbies:}}
    \small{Singing and enjoying music - \href{https://vishuragams.pages.dev}{\underline{Carnatic Ragas}}, playing \href{https://vishugp.github.io/Thuruppu/}{\underline{card games}} and badminton, robotics}
    }
\end{itemize}

%-----------CERTIFICATIONS-----------
\vspace{-21pt}
\section{\Large{Certifications}}
\vspace{5pt}
\resumeItemListStart
\resumeItem{AWS Certified Solutions Architect – Associate, Amazon Web Services\hfill{May 2025}}
\resumeItem{\vspace{-5pt}AWS Certified Machine Learning – Specialty, Amazon Web Services \hfill{expected Jun 2025}}

\resumeItemListEnd

\end{document}
